### 2020-04-08 system-model.tex
:pencil: Construct frequency-selective IRS

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times LN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $L$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $L$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,L,n}^T]^T \in \mathbb{C}^{L \times M}$, with $\boldsymbol{h}_{I,l,n}=[h_{I,l,n,1},\dots,h_{I,l,n,M}] \in \mathbb{C}^{1 \times M}$. We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,L,n,m}]^T \in \mathbb{C}^{L \times 1}$ to represent the channel between antenna $m$ and the IRS. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_l e^{j \theta_l}$, where $\beta_l \in [0,1]$ and $\theta_l \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{LN \times L}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{\Theta} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
		\begin{equation}	\label{eq:h_{k,n}}
			\begin{split}
				\boldsymbol{h}_{k,n}
				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{H}_{I,n}	\\
				&=[h_{k,n,1},\dots,h_{k,n,M}]
			\end{split}
		\end{equation}
		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n,m}$.
	\end{subsection}

>>>>

		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links are $\boldsymbol{h}_{D,n}=[h_{D,n,1},\dots,h_{D,n,K}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{h}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$, with $\boldsymbol{h}_{R,n,l}=[h_{R,n,l,1},\dots,h_{R,n,l,k}]^T \in \mathbb{C}^{K \times 1}$. 'Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting all reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}	\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
		\begin{equation}	\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_D+\boldsymbol{H}_{R}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		It is interesting to notice that the reflective channel across all $N$ subbands influences the overall frequency response at subband $n$.
	\end{subsection}
